% 重新定义摘要环境
\begin{ChineseAbstract}
    本模板是为上海工程技术大学学士学位本科毕业设计论文编写的 \LaTeX{} 模板, 旨在让大家专注于    论文的内容写作, 而不用花费过多精力在格式的定制和调整上. 本手册是相应的参考, 其中提供了一些环境和命令可以让模板的使用更为方便. 同时需要注意, 使用者需要有一定的 \LaTeX{} 的使用经验, 至少要会使用 ctex 宏包的一些功能, 比如调节字距或修改字体大小等等.

    这里提供有基本的毕业设计论文的模板，所以可以通过对比Word模板进行适当的调节，经过多次测试发现Latex模板设置并不完全和Word模板一致，最终得到的效果要符合学校毕业论文的要求，并且看起来美观大方，顺利通过毕业设计答辩、盲审等等一系列流程是最为重要的。
    
    上海工程技术大学学士学位毕业设计论文latex模板更新地址详细参见\href{https://github.com/MobtgZhang/sues-thesis-bachelor}{GitHub}。
    % 若摘要比较短，可以通过下面命令调节关键字位置
    \vspace{0.1\textheight}

    \ChineseKeywords{排版系统，强大功能，文档说明}
\end{ChineseAbstract}

\newpage
\begin{EnglishAbstract}
    The template provided here is a \LaTeX{} template designed for the bachelor's degree undergraduate design thesis at Shanghai University of Engineering Science.
    Its purpose is to allow users to focus on the content of their thesis writing without having to spend too much time on customizing and adjusting the formatting.
    This manual serves as a reference, providing some environments and commands to make the use of the template more convenient.
    It is important to note that users should have some experience with \LaTeX{}, at least in using certain functions of the ctex package, such as adjusting letter spacing or modifying font sizes.

    Here, we provide a basic template for the undergraduate design thesis, so it can be adjusted appropriately by comparing it with the Word template.
    After multiple tests, it has been found that the settings in the \LaTeX{} template are not completely consistent with the Word template.
    The ultimate goal is to meet the requirements of the university's graduation thesis and have an aesthetically pleasing appearance,
    ensuring a smooth process through the defense and blind review of the design thesis, among other procedures.

    For detailed information on the update address of the \LaTeX{} template for the bachelor's degree graduation design thesis at Shanghai University of Engineering Science, please refer to the \href{https://github.com/MobtgZhang/sues-thesis-bachelor}{GitHub} page.
    % 若摘要比较短，可以通过下面命令调节关键字位置
    \vspace{0.1\textheight}
    
    \EnglishKeywords{Typesetting system, Powerful functions, Document Description}
\end{EnglishAbstract}

\newpage
